Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-24 doc/bcspaper/article.tex
Very close to fitting everything onto 6 pages

\abstract*{Partridge is a system that enables intelligent search for
  academic papers by allowing users to query terms within
  sentences designating a particular core scientific concept (e.g. Hypothesis, Result, etc). 
  The system also automatically classifies papers according to
  article types (e.g. Review, Case Study). Here we focus on the latter
  aspect of the system. For each paper, Partridge automatically
  extracts the full paper content from PDF files, converts it to XML,
  determines sentence boundaries, automatically labels the sentences
  with core scientific concepts, and then uses a random forest model to
  classify the paper type. We show that the type of a paper can be
  reliably predicted by a model which analyses the distribution of
  core scientific concepts within the sentences of the paper. We
  discuss the appropriateness of many of the existing paper types used
  by major journals, and their corresponding distributions. Partridge
  is online and available for use, includes a browser-friendly
  bookmarklet for new paper submission, and demonstrates a range of
  possibilities for more intelligent search in the scientific
  literature. The Partidge instance can be used at
  \url{http://farnsworth.papro.org.uk}, and further information about
  the project can be found at \url{http://papro.org.uk}}

\section{Introduction} \label{sec:1} Since the advent of the `Digital Age' and
the ability of computers to copy and reproduce information for a negligible
cost, the amount of information available to researchers has been increasing
drastically. As available information increases, relevant material becomes
progressively more difficult to find manually and the need for an automated
information retrieval tool more apparent. There are already a large number of
information retrieval and recommendation systems for scientific publications.
Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}),
the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
(\url{http://www.textpresso.org/}) index only publications from predefined
journals or topics (for the above examples, Agriculture, Biology and
Bioinformatics respectively).  Unfortunately, these domain specific indexing
systems usually only contain a small subset of papers, excluding potentially
crucial literature because it does not quite fit into the subject domain.

@@

\section{Methods}
\label{sec:2}
%how types were chosen,

@@

\subfloat[]{
\includegraphics[width=0.48\textwidth]{figures/review_corescs.png}
}
\subfloat[]{
\includegraphics[width=0.48\textwidth]{figures/report_corescs.png}
}
\caption{The CoreSC content of a review paper and a research paper randomly selected from the corpus}

@@

\section{Results and Discussion}
\label{sec:3}

@@

\begin{wraptable}{l}{0.65\textwidth}
\vspace{-20pt}

\begin{tabular}{p{2.4cm}p{1.5cm}p{1.5cm}p{1.5cm}}
\hline\noalign{\smallskip}
Classes & Recall & Precision & F-measure  \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Case Study      &   24.3\verb|%|    &    24.5\verb|%|     &   24.4\verb|%| \\
Correspondence  &   {\bf  54.5\verb|%|}    &    {\bf 50.5\verb|%|}    &    {\bf 52.4\verb|%|} \\ 
Essay           &   45.0\verb|%|     &   46.2\verb|%|    &    45.6\verb|%| \\
Opinion         &   24.7\verb|%|    &    23.5\verb|%|  &      24.1\verb|%| \\   
Perspective     &   25.5\verb|%|  &      30.4\verb|%|  &       27.7\verb|%| \\
Research        &   {\bf 70.0\verb|%|}    &    {\bf 61.9\verb|%|}    &    {\bf 65.7\verb|%|} \\
Review          &  {\bf 63.1\verb|%|}     &   {\bf 62.5\verb|%|}     &   {\bf 62.8\verb|%|} \\
Viewpoint       &     14.9\verb|%|     &   15.7\verb|%|  &      15.3\verb|%| \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
\label{tab:recallPrecision}       % Give a unique label
\vspace{-30pt}
\end{wraptable}

@@

\begin{table}
\caption{Confusion matrix summed over 10-fold cross validation, reporting the results on the held-out validation segment. Rows represent true classes, columns represent predicted classes.}
\label{tab:confusion}       % Give a unique label
\begin{tabular}{lllllllll}
\hline\noalign{\smallskip}
      &  Case Study   &     Corresp.      &   Essay  & Opinion &     Perspective    &     Research    &     Review  & Viewpoint \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Case Study    &    26   &     2     &   11    &    2  &      5 & 26       & 25 &       10 \\
Correspondence  &      4  &      54   &     3    &    9     &   15 & 8   &     4 &       2 \\
Essay      &  8     &   5    &   90    &    2 &       39      &  5 & 46    &    5 \\
Opinion    &    4   &     7 &       2   &     23      &  27     &   10   &  3  &      17 \\
Perspective &       11  &      16    &    49       & 30      &  51 & 6      &  26    &   11 \\
Research      &  19    &    6 &       2 &       8    &    5      &  140  &   12    &    8\\
Review       & 27     &   8     &   35    &    5      &  13    &    21   &  197 &       6\\
Viewpoint    &    7  &      9   &     3     &   19     &   13 & 10     &   2  &      11 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

@@

\section{Conclusion}
\label{sec:4}

@@

\bibliographystyle{plain}
\bibliography{partridge}

>>>>

\abstract{Partridge is a system that enables intelligent search for
  academic papers by allowing users to query terms within
  sentences designating a particular core scientific concept (e.g. Hypothesis, Result, etc). 
  The system also automatically classifies papers according to
  article types (e.g. Review, Case Study). Here we focus on the latter
  aspect of the system. For each paper, Partridge automatically
  extracts the full paper content from PDF files, converts it to XML,
  determines sentence boundaries, automatically labels the sentences
  with core scientific concepts, and then uses a random forest model to
  classify the paper type. We show that the type of a paper can be
  reliably predicted by a model which analyses the distribution of
  core scientific concepts within the sentences of the paper. We
  discuss the appropriateness of many of the existing paper types used
  by major journals, and their corresponding distributions. Partridge
  is online and available for use, includes a browser-friendly
  bookmarklet for new paper submission, and demonstrates a range of
  possibilities for more intelligent search in the scientific
  literature. The Partidge instance can be used at
  \url{http://farnsworth.papro.org.uk}, and further information about
  the project can be found at \url{http://papro.org.uk}}

\vspace{-15pt}
\section{Introduction} \label{sec:1}

Since the advent of the `Digital Age', the amount of information available to
researchers has been increasing drastically and relevant material is becoming
progressively more difficult to find manually and the need for an automated
information retrieval tool more apparent. There are already a large number of
information retrieval and recommendation systems for scientific publications.
Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}),
the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
(\url{http://www.textpresso.org/}) index only publications from predefined
journals or topics (for the above examples, Agriculture, Biology and
Bioinformatics respectively).  Unfortunately, these domain specific indexing
systems usually only contain a small subset of papers, excluding potentially
crucial literature because it does not quite fit into the subject domain.

@@

\vspace{-15pt}
\section{Methods}
\label{sec:2}
%how types were chosen,

@@

\subfloat{
\includegraphics[width=0.45\textwidth]{figures/review_corescs.png}
}
\subfloat{
\includegraphics[width=0.45\textwidth]{figures/report_corescs.png}
}
\caption{The CoreSC content of a review paper and a research paper randomly selected from the corpus}

@@

\vspace{-15pt}
\section{Results and Discussion}
\label{sec:3}

\begin{table}

\begin{tabular}{p{2.4cm}p{1.5cm}p{1.5cm}p{1.5cm}}
\hline\noalign{\smallskip}
Classes & Recall & Precision & F-measure  \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Case Study      &   24.3\verb|%|    &    24.5\verb|%|     &   24.4\verb|%| \\
Correspondence  &   {\bf  54.5\verb|%|}    &    {\bf 50.5\verb|%|}    &    {\bf 52.4\verb|%|} \\ 
Essay           &   45.0\verb|%|     &   46.2\verb|%|    &    45.6\verb|%| \\
Opinion         &   24.7\verb|%|    &    23.5\verb|%|  &      24.1\verb|%| \\   
Perspective     &   25.5\verb|%|  &      30.4\verb|%|  &       27.7\verb|%| \\
Research        &   {\bf 70.0\verb|%|}    &    {\bf 61.9\verb|%|}    &    {\bf 65.7\verb|%|} \\
Review          &  {\bf 63.1\verb|%|}     &   {\bf 62.5\verb|%|}     &   {\bf 62.8\verb|%|} \\
Viewpoint       &     14.9\verb|%|     &   15.7\verb|%|  &      15.3\verb|%| \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}

\vspace{-20pt}
\label{tab:recallPrecision}       % Give a unique label
\end{table}

@@

@@

\begin{table}

\vspace{-10pt}

\caption{Confusion matrix summed over 10-fold cross validation, reporting the results on the held-out validation segment. Rows represent true classes, columns represent predicted classes.}
\label{tab:confusion}       % Give a unique label]

\begin{tabular}{lllllllll}
\hline\noalign{\smallskip}
      &  Case Study   &     Corresp.      &   Essay  & Opinion &     Perspective    &     Research    &     Review  & Viewpoint \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Case Study    &    26   &     2     &   11    &    2  &      5 & 26       & 25 &       10 \\
Correspondence  &      4  &      54   &     3    &    9     &   15 & 8   &     4 &       2 \\
Essay      &  8     &   5    &   90    &    2 &       39      &  5 & 46    &    5 \\
Opinion    &    4   &     7 &       2   &     23      &  27     &   10   &  3  &      17 \\
Perspective &       11  &      16    &    49       & 30      &  51 & 6      &  26    &   11 \\
Research      &  19    &    6 &       2 &       8    &    5      &  140  &   12    &    8\\
Review       & 27     &   8     &   35    &    5      &  13    &    21   &  197 &       6\\
Viewpoint    &    7  &      9   &     3     &   19     &   13 & 10     &   2  &      11 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}]
\vspace{-15pt}
\end{table}

@@

\vspace{-15pt}
\section{Conclusion}
\label{sec:4}

@@

\vspace{-15pt}
\bibliographystyle{plain}
\bibliography{partridge}
